An Improved Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2021-09-27 simplified_sdc_intro/paper.tex
more updates

    \item predict $\qb$ to the interfaces at $t^{n+1/2}$ using the CTU PPM
      method.  The source terms, $\Sq$, used in the prediction are:
      \begin{equation}
        \Sc(\qb) = \Hb(\qb) + \Ic_\qb^{n+1/2,(k-1)}
      \end{equation}
      Here we use the iteratively lagged integrals of the primitive variable
      terms accounting only for reactions, $\Ic_\qb^{n+1/2,(k-1)}$, as the
      reactive source.  This is in contrast to Strang-splitting, where no
      explicit reactive source terms are seen by the hydrodynamics update.
      Any hydrodynamic source terms are time-centered
      using the previous iteration:
\MarginPar{Formally both $t^n$ or $t^{n+1/2}$ sources give you 2nd-order since they are CTU predictor source terms.  I've never found this type of iteration for this term to amount to any benefit}
      \begin{equation}
        \Sqhydro^{n+1/2} = \frac{1}{2} \left ( \Sqhydro^n + \Sqhydro^{n+1,(k-1)} \right )
      \end{equation}

      In the unsplit CTU method \citep{ppmunsplit}, the interface
      states used for the final Riemann problem through the zone
      interface consist of a normal predictor and a transverse flux
      correction.  We can add the source terms either to the normal
      predictor (for example, doing characteristic tracing as
      described in \citealt{ppm}) or after all of the transverse flux
      corrections are made.  Both are second-order accurate.  For the
      hydrodynamics sources, we do those in the normal predictor.
      However, for the reactive sources, we found that it is most
      reliable to add them at the end of the interface state
      construction, after the transverse flux corrections.  This is
      because we want to ensure that sum over species of $\Ic_\qb$ is
      zero, and characteristic tracing or the various flux corrections
      may not preserve this.

      {\color{red} We enforce that the species interface states remain in $[0, 1]$ after adding the reactive source.}

>>>>

    \item predict $\qb$ to the interfaces at $t^{n+1/2}$ using the CTU PPM
      method.  The source terms, $\Sq$, used in the prediction are:
      \begin{equation}
        \Sc(\qb) = \Hb(\qb) + \Ic_\qb^{n+1/2,(k-1)}
      \end{equation}
      Here we use the iteratively lagged integrals of the primitive variable
      terms accounting only for reactions, $\Ic_\qb^{n+1/2,(k-1)}$, as the
      reactive source.  This is in contrast to Strang-splitting, where no
      explicit reactive source terms are seen by the hydrodynamics update.
%%       Any hydrodynamic source terms are time-centered
%%       using the previous iteration:
%% \MarginPar{Formally both $t^n$ or $t^{n+1/2}$ sources give you 2nd-order since they are CTU predictor source terms.  I've never found this type of iteration for this term to amount to any benefit}
%%       \begin{equation}
%%         \Sqhydro^{n+1/2} = \frac{1}{2} \left ( \Sqhydro^n + \Sqhydro^{n+1,(k-1)} \right )
%%       \end{equation}

      In the unsplit CTU method \citep{ppmunsplit}, the interface
      states used for the final Riemann problem through the zone
      interface consist of a normal predictor and a transverse flux
      correction.  We can add the source terms either to the normal
      predictor (for example, doing characteristic tracing as
      described in \citealt{ppm}) or after all of the transverse flux
      corrections are made.  Both are second-order accurate.  For the
      hydrodynamics sources, we do those in the normal predictor.
      However, for the reactive sources, we found that it is most
      reliable to add them at the end of the interface state
      construction, after the transverse flux corrections.  This is
      because we want to ensure that sum over species of $\Ic_\qb$ is
      zero, and characteristic tracing or the various flux corrections
      may not preserve this.  We enforce that the species interface
      states remain in $[0, 1]$ after adding the reactive source.
